Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-03-03 LaTeX/paper.tex
Fixed my address lol
Updated reference

  Some of the major limitations for applied quantum computing are 
  the number of qubits required to perform a given task, the likelihood of errors
  in measurement, and the overhead associated with running circuits on real-world
  quantum computers.

@@

  Furthermore, the longer-term goal is to identify the types of algorithms that 
  likewise may have significant quantum advantage based upon reversible functions.

  Grover's algorithm can be used to provide a very efficient search, 
  which is in essence a content addressable memory that works at a scale limited only by qubit scaling.

  One of the major intentions for this paper is demonstration of the broad utility of Grover's 
  algorithm, and to provide a general reference
  for how Grover's algorithm may be used to invert a given function.

@@

  If a quantum computer makes SP factoring as simple as SP computation, given a 
  reversible quantum circuit, then this means all encryption can potentially 
  be broken by such a quantum circuit.

@@

  For example, the RSA number 250, which is 892-bits long, was only recently factored using a parallel computer. 
  The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.

  However, a quantum computer has a much lower time complexity if the number of qubits
  can be scaled to implement a quantum circuit that can factor a semiprime. Ongoing research
  at China State Key Laboratories suggests that they have been making significant
  progress in breaking RSA encryption, considering their 48-bit demo using 10 qubits
  in 2022~\cite{yan2022factoringintegerssublinearresources}. Furthermore, they claim
  that with the techniques they have been using, it would be possible to break
  RSA 2048 with a quantum circuit which needs only 372 qubits, far less than the
  1,121 qubit machine currently available in the United 
  States with IBM's Condor~\cite{abughanem2024ibmquantumcomputersevolution}.

@@

% LaTeX inserts the ``Address for correspondence'' heading.
\begin{correspondence}
Jacob Collins\\
1565 Filbert Ave\\
jbcollins@csuchico.edu
\end{correspondence}

>>>>

  % Some of the major limitations for applied quantum computing are 
  % the number of qubits required to perform a given task, the likelihood of errors
  % in measurement, and the overhead associated with running circuits on real-world
  % quantum computers.

@@

  One of the major intentions for this paper is demonstration of the broad utility of Grover's 
  algorithm.%, and to provide a general reference
  %for how Grover's algorithm may be used to invert a given function.

  Furthermore, the longer-term goal is to identify the types of algorithms that 
  likewise may have significant quantum advantage based upon reversible functions.
  % Grover's algorithm can be used to provide a very efficient search, 
  % which is in essence a content addressable memory that works at a scale limited only by qubit scaling.

@@

  % If a quantum computer makes SP factoring as simple as SP computation, given a 
  % reversible quantum circuit, then this means all encryption can potentially 
  % be broken by such a quantum circuit.

@@

  For example, the RSA number 250, which is 892-bits long, was only recently 
  factored using a parallel computer with the best known SP factoring 
  method known right now~\cite{Bai2016}.

  The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.

  However, a quantum computer has a much lower time complexity if the number of qubits
  can be scaled to implement a quantum circuit that can factor a semiprime. Ongoing research
  at China State Key Laboratories suggests that they have been making significant
  progress in breaking RSA encryption, considering their 48-bit demo using 10 qubits
  in 2022~\cite{yan2022factoringintegerssublinearresources}.

  Furthermore, they claim
  that with the techniques they have been using, it would be possible to break
  RSA 2048 with a quantum circuit which needs only 372 qubits, far less than the
  1,121 qubit machine currently available in the United 
  States with IBM's Condor~\cite{abughanem2024ibmquantumcomputersevolution}.

@@

% LaTeX inserts the ``Address for correspondence'' heading.
\begin{correspondence}
Jacob Collins\\
1565 Filbert Avenue, Chico, CA 95926\\
jbcollins@csuchico.edu
\end{correspondence}
